Assessing the Multifaceted Influences on Current Coffee Prices

### 2024-11-29 paper/paper.qmd
Update Readme
Update ReadME and delete file that is not be used.

```{r}
#| label: fig-Hist-of-current-price
#| fig-cap: "Histogram of Current Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-Hist-of-old-price
#| fig-cap: "Histogram of Old Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-Bar-plot-of-old-price
#| fig-cap: "Bar Plot of Old Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-scatter-plot-of-current-vs-old-price
#| fig-cap: "Scatterplot of Current Price vs Old Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-barplot-of-old-price
#| fig-cap: "Boxplot of Current Price by Vendor"
#| message: false
#| echo: false

@@

@tbl-model-summary indicates a robust fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices. The model's parameters show that the old price of coffee (coefficient = 0.77) has a significant positive influence on the current price, suggesting that past pricing trends are good predictors of current pricing strategies. Vendor impact, specifically SaveOnFoods, shows a negative association with current price (coefficient = -0.61), indicating that coffee products from SaveOnFoods tend to be cheaper compared to Metro. Additionally, the month coefficient (0.06) implies a slight monthly variation in coffee pricing. The model's predictive performance is validated by low WAIC and LOOIC scores, and a small RMSE of 1.75, enhancing confidence in the reliability of its predictions.

@@

```{r}
#| label: fig-credibility-interval
#| fig-cap: "credibility interval"
#| eval: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-trace-plot
#| fig-cap: "Trace plot"
#| eval: true
#| echo: false
#| warning: false
#| message: false

plot(Coffee_product_pricing, "trace")

@@

```{r}
#| label: fig-rhat-plot
#| fig-cap: "R-hat plot"
#| eval: true
#| echo: false
#| warning: false
#| message: false

>>>>

```{r}
#| label: fig-Hist-of-current-price
#| fig-cap: "Frequency of Current Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-Hist-of-old-price
#| fig-cap: "Frequency of Old Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-Bar-plot-of-vendor
#| fig-cap: "Frequency of Vendor"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-scatter-plot-of-current-vs-old-price
#| fig-cap: "Current Price vs Old Price"
#| message: false
#| echo: false

@@

```{r}
#| label: fig-barplot-of-old-price
#| fig-cap: "Current Price by Vendor"
#| message: false
#| echo: false

@@

@tbl-model-summary indicates a strong fit with a high $R^2$ of 0.900, suggesting a strong explanatory power of the model regarding the variance in coffee product prices. The model's parameters show that the old price of coffee (coefficient = 0.77) has a significant positive influence on the current price, suggesting that past pricing trends are good predictors of current pricing strategies. Vendor impact, specifically SaveOnFoods, shows a negative association with current price (coefficient = -0.61), indicating that coffee products from SaveOnFoods tend to be cheaper compared to Metro. Additionally, the month coefficient (0.06) implies a slight monthly variation in coffee pricing. The model's predictive performance is validated by low WAIC and LOOIC scores, and a small RMSE of 1.75, enhancing confidence in the reliability of its predictions.

@@

```{r}
#| label: fig-credibility-interval
#| fig-cap: "Credibility Interval of Coffee products pricing"
#| eval: true
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-trace-plot
#| fig-cap: "Trace plot of Coffee products pricing"
#| eval: true
#| echo: false
#| warning: false
#| message: false

plot(Coffee_product_pricing, "trace")
```

```{r}

#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-trace-plot
#| fig-cap: "Trace plot of Party"
#| fig-subcap: ["Trace plot of Intercept", "Trace plot of old_price", "Trace plot of month", "Trace plot of vendor: SaveOnFoods"]
#| layout-ncol: 3

plot(Coffee_product_pricing, "trace", "(Intercept)")
plot(Coffee_product_pricing, "trace", "old_price")
plot(Coffee_product_pricing, "trace", "month")
plot(Coffee_product_pricing, "trace", "vendorSaveOnFoods")

@@

```{r}
#| label: fig-rhat-plot
#| fig-cap: "R-hat plot of Coffee products pricing"
#| eval: true
#| echo: false
#| warning: false
#| message: false
